---
title: "OCS soil health analysis"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load libraries

```{r message=FALSE, warning=FALSE}

#Load packages 
library(tidyverse) ##install.packages("tidyverse")
library(knitr)
library(patchwork) ##install.packages("patchwork")
library(skimr)     ##install.packages("skimr")
library(readxl)
library(janitor) ##install.packages("janitor")
library(kableExtra) ##install.packages("kableExtra")
library(viridis) ##install.packages("viridis")
library(lme4) ##install.packages("lme4")
library(lmerTest) ##install.packages("lmerTest")
library(emmeans) ##install.packages("emmeans")
library(rstatix) ##install.packages("rstatix")
#library(Matrix) ##install.packages("Matrix")
library(multcomp) ##install.packages("multcomp")
library(multcompView) ##install.packages("multcompView")
library(ggResidpanel) ##install.packages("ggResidpanel")
#library(car)
#library(TMB)  ##install.packages("TMB")
library(WrensBookshelf)##install.packages("WrensBookshelf")
library(magrittr)
library(grid)
library(hues) ##install.packages("hues")
library(vegan) ##install.packages("vegan")
library(permute)
library(ggrepel) ##install.packages("ggrepel")
library(ggordiplots) ##install.packages("ggordiplots")
library(FD) ##install.packages("FD")
library(ade4)
library(gawdis)  ##install.packages("gawdis")
## For GLM modeling
install.packages("devtools")  # Install devtools if not already installed
library(devtools)  
install_github("singmann/monet")  # Install monet from GitHub
library(monet)  # Load the package
library(glmmTMB)  ##install.packages("glmmTMB")
library(DHARMa)  ##install.packages("DHARMa")
library(performance) ##install.packages("performance")
library(corrplot) # for testing species x CWM
#library(Hmisc) # for testing species x CWM
library(broom.mixed) ##install.packages("broom.mixed")
library(purrr)  # ##install.packages("purr")

#Load Functions
MeanPlusSe<-function(x) mean(x)+plotrix::std.error(x)

find_logw0=function(x){c=trunc(log(min(x[x>0],na.rm=T)))
d=exp(c)
return(d)}
```

<br>

# Load and clean data

## Load data

``` {r}
ocs_soil_health_raw <- read_excel("~/Github/OCS-microinvertebrates/ocs_soil_health_2022.xlsx")
ocs_soil_health_raw$block <- as.factor(ocs_soil_health_raw$block)
ocs_soil_health_raw$entry <- as.factor(ocs_soil_health_raw$entry)
ocs_soil_health_raw$treatments <- as.factor(ocs_soil_health_raw$treatments)



kable(head(ocs_soil_health_raw))

```

##Clean data

```{r}
 #Filter relevant data (we can't use data from alley and corn)
ocs_soil_health_clean <- ocs_soil_health_raw |>  
  filter(treatments %in% c("HF", "LF", "EWM", "RT"))

# Display cleaned dataset
kable(head(ocs_soil_health_clean))


```
#Model testing
##pred_water_capacity
```{r}
pred_water_capacity.gauss<- glmmTMB(pred_water_capacity~ treatments * entry + block + (1 | block:treatments),
                      data = ocs_soil_health_clean,
                      family = gaussian())

pred_water_capacity.gamma <- glmmTMB(pred_water_capacity ~ treatments * entry + block + (1 | block:treatments),
                                     data = ocs_soil_health_clean,
                                     family = Gamma(link = "log"))

#look at the AIC
AIC(pred_water_capacity.gauss,pred_water_capacity.gamma )
logLik(pred_water_capacity.gamma)

ocs_soil_health_clean <- ocs_soil_health_clean |> 
  mutate(pred_water_capacity_scaled = pred_water_capacity * 100)

pred_water_capacity.gauss <- glmmTMB(pred_water_capacity_scaled ~ treatments * entry + block + (1 | block:treatments),
                                     data = ocs_soil_health_clean,
                                      family = gaussian())

AIC(pred_water_capacity.gauss) 

# The simulate residuals function comes from DHARMa and allows visual inspection of
# glmm fit. Another useful way of deciding which model you will use for this response variable.
simulateResiduals(pred_water_capacity.gauss,plot = TRUE) 

check_model(pred_water_capacity.gauss)


```

###monet annova 
###not significant
```{r}
# `test_terms` is from monet and allows for a Type III anova for glmmTMB
pred_water_capacity.gauss.anova <- test_terms(formula = pred_water_capacity~ treatments * entry + block, # fixed effects go here
                                   data = ocs_soil_health_clean,
                                   extra_formula = ~ (1|block:treatments), # random effects go here
                                   fit_fun = glmmTMB,
                                   fit_arg = list(family = gaussian())); pred_water_capacity.gauss.anova  # put the family you decided on in the fit_arg
```

##surface_hardness
```{r}
surface_hardness.gauss<- glmmTMB(surface_hardness~ treatments * entry + block + (1 | block:treatments),
                      data = ocs_soil_health_clean,
                      family = gaussian())

surface_hardness.gamma <- glmmTMB(surface_hardness~ treatments * entry + block + (1 | block:treatments),
                                     data = ocs_soil_health_clean,
                                     family = Gamma(link = "log"))

#look at the AIC
AIC(surface_hardness.gauss,surface_hardness.gamma )


ocs_soil_health_clean <- ocs_soil_health_clean |> 
  mutate(pred_water_capacity_scaled = pred_water_capacity * 100)

pred_water_capacity.gauss <- glmmTMB(pred_water_capacity_scaled ~ treatments * entry + block + (1 | block:treatments),
                                     data = ocs_soil_health_clean,
                                      family = gaussian())

AIC(pred_water_capacity.gauss) 

# The simulate residuals function comes from DHARMa and allows visual inspection of
# glmm fit. Another useful way of deciding which model you will use for this response variable.
simulateResiduals(surface_hardness.gamma,plot = TRUE) 

check_model(surface_hardness.gamma)


```

###monet annova 
###significant

```{r}
#`test_terms` is from monet and allows for a Type III anova for glmmTMB

surface_hardness.gamma.anova <- test_terms(formula = surface_hardness~ treatments * entry +block, #fixed effects go here
                                   data = ocs_soil_health_clean,
                                   extra_formula = ~ (1|block:treatments), # random effects go here
                                   fit_fun = glmmTMB,
                                   fit_arg = list(Gamma(link = "log"))); surface_hardness.gamma.anova  # put the family you decided on in the fit_arg
```

```{r}
# Then move on to post-hoc using emmeans if indicated by the ANOVA. The example below would be used if the System term
# alone was significant.
surface_hardness.emm <- emmeans(surface_hardness.gamma, ~treatments|entry, type="response"); pwpm(surface_hardness.emm , adjust="none")


```
```{r}
# Compute estimated marginal means for treatments within each entry
surface_hardness.emm <- emmeans(surface_hardness.gamma, ~treatments | entry, type = "response")

# Generate CLD output
cld_surface_hardness <- cld(surface_hardness.emm, Letters = letters, adjust = "none", sort = TRUE, reversed = TRUE)

# Print the results
cld_surface_hardness

```
##subsurface_hardness
```{r}
subsurface_hardness.gauss<- glmmTMB(subsurface_hardness~ treatments * entry + block + (1 | block:treatments),
                      data = ocs_soil_health_clean,
                      family = gaussian())

subsurface_hardness.gamma <- glmmTMB(subsurface_hardness~ treatments * entry + block + (1 | block:treatments),
                                     data = ocs_soil_health_clean,
                                     family = Gamma(link = "log"))

#look at the AIC
AIC(subsurface_hardness.gauss,subsurface_hardness.gamma )


ocs_soil_health_clean <- ocs_soil_health_clean |> 
  mutate(pred_water_capacity_scaled = pred_water_capacity * 100)

pred_water_capacity.gauss <- glmmTMB(pred_water_capacity_scaled ~ treatments * entry + block + (1 | block:treatments),
                                     data = ocs_soil_health_clean,
                                      family = gaussian())

AIC(pred_water_capacity.gauss) 

# The simulate residuals function comes from DHARMa and allows visual inspection of
# glmm fit. Another useful way of deciding which model you will use for this response variable.
simulateResiduals(subsurface_hardness.gamma,plot = TRUE) 

check_model(subsurface_hardness.gamma)


```
###monet annova 
###significant

```{r}
#`test_terms` is from monet and allows for a Type III anova for glmmTMB

subsurface_hardness.gamma.anova <- test_terms(formula = subsurface_hardness~ treatments * entry +block, #fixed effects go here
                                   data = ocs_soil_health_clean,
                                   extra_formula = ~ (1|block:treatments), # random effects go here
                                   fit_fun = glmmTMB,
                                   fit_arg = list(Gamma(link = "log"))); subsurface_hardness.gamma.anova  # put the family you decided on in the fit_arg
```
```{r}
# Then move on to post-hoc using emmeans if indicated by the ANOVA. The example below would be used if the System term
# alone was significant.
subsurface_hardness.emm <- emmeans(subsurface_hardness.gamma, ~treatments|entry, type="response"); pwpm(subsurface_hardness.emm , adjust="none")


```
```{r}
# Compute estimated marginal means for treatments within each entry
subsurface_hardness.emm <- emmeans(subsurface_hardness.gamma, ~treatments | entry, type = "response")

# Generate CLD output
cld_subsurface_hardness <- cld(subsurface_hardness.emm, Letters = letters, adjust = "none", sort = TRUE, reversed = TRUE)

# Print the results
cld_subsurface_hardness

```
# organic_matter(is a percentage)
```{r}



organic_matter.beta <- glmmTMB(organic_matter / 100 ~ treatments * entry + block + (1 | block:treatments),
                                    data = ocs_soil_health_clean,
                                    family = beta_family())




# The simulate residuals function comes from DHARMa and allows visual inspection of
# glmm fit. Another useful way of deciding which model you will use for this response variable.
simulateResiduals(organic_matter.beta,plot = TRUE) 

check_model(organic_matter.beta)


```
###monet annova 
###Not significant

```{r}
#`test_terms` is from monet and allows for a Type III anova for glmmTMB

# Scale organic matter percentage to (0,1)
ocs_soil_health_clean$organic_matter_scaled <- ocs_soil_health_clean$organic_matter / 100

# Fit beta regression
organic_matter.beta.anova <- test_terms(
  formula = organic_matter_scaled ~ treatments * entry + block,  # Fixed effects
  data = ocs_soil_health_clean,
  extra_formula = ~ (1|block:treatments),  # Random effects
  fit_fun = glmmTMB,
  fit_arg = list(family = beta_family())
)

organic_matter.beta.anova
```

##pred_soil_protein
```{r}
pred_soil_protein.gauss<- glmmTMB(pred_soil_protein~ treatments * entry + block + (1 | block:treatments),
                      data = ocs_soil_health_clean,
                      family = gaussian())





pred_soil_protein.gamma <- glmmTMB(pred_soil_protein~ treatments * entry + block + (1 | block:treatments),
                                     data = ocs_soil_health_clean,
                                     family = Gamma(link = "log"))


#look at the AIC
AIC(pred_soil_protein.gauss,pred_soil_protein.gamma )



# The simulate residuals function comes from DHARMa and allows visual inspection of
# glmm fit. Another useful way of deciding which model you will use for this response variable.
simulateResiduals(pred_soil_protein.gamma,plot = TRUE) 

check_model(pred_soil_protein.gamma)


```
###monet annova 
### Notsignificant

```{r}
#`test_terms` is from monet and allows for a Type III anova for glmmTMB

pred_soil_protein.gamma.anova <- test_terms(formula = pred_soil_protein~ treatments * entry +block, #fixed effects go here
                                   data = ocs_soil_health_clean,
                                   extra_formula = ~ (1|block:treatments), # random effects go here
                                   fit_fun = glmmTMB,
                                   fit_arg = list(Gamma(link = "log"))); pred_soil_protein.gamma.anova # put the family you decided on in the fit_arg
```





#Loop attempt

```{r}
## Select column names from soil_texture_sand to overall_score
soil_health_params <- names(ocs_soil_health_clean)[8:45]

# Create an empty list to store model results
soil_health_models <- list()

# Loop through each soil health parameter and fit the model
for (param in soil_health_params) {
  formula <- as.formula(paste(param, "~ treatments * entry + block + (1 | block:treatments)"))
  
  # Fit the model
  soil_health_models[[param]] <- glmmTMB(formula, 
                                         data = ocs_soil_health_clean, 
                                         family = gaussian())
}

# Print summaries for all models
walk2(soil_health_models, names(soil_health_models), ~ {
  cat("\n*** Summary for:", .y, "***\n")
  print(summary(.x))
})

```




### Joint test (anova)
```{r}
glmm_ja |> 
  joint_tests() |> 
  kable()  
```

### Fisher compact letter display
####  treatments (significant)

```{r}
cld_treatments_fisher <-cld(emmeans(glmm_ja, ~  treatments , type = "response"), Letters = letters, adjust = "none",sort = TRUE, reversed=TRUE)
cld_treatments_fisher 
```