---
title: "OCS soil health analysis"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load libraries

```{r message=FALSE, warning=FALSE}

library(tidyverse)
library(multcomp)
library(emmeans)
library(knitr)
library(patchwork) ##install.packages("patchwork")
library(skimr)     ##install.packages("skimr")
library(readxl)
library(janitor) ##install.packages("janitor")
library(kableExtra) ##install.packages("kableExtra")
library(WrensBookshelf)##install.packages("WrensBookshelf")
## For GLM modeling
library(monet)
library(DHARMa)
library(glmmTMB)
library(performance)
```

<br>

# Load and clean data

## Load data

``` {r}
ocs_soil_health_raw <- read_excel("~/Github/OCS_microarthropods/raw-data/ocs_soil_health_2022.xlsx")
ocs_soil_health_raw$block <- as.factor(ocs_soil_health_raw$block)
ocs_soil_health_raw$entry <- as.factor(ocs_soil_health_raw$entry)
ocs_soil_health_raw$system <- as.factor(ocs_soil_health_raw$system)



kable(head(ocs_soil_health_raw))

```

##Clean data

```{r}
 #Filter relevant data (we can't use data from alley and corn)
ocs_soil_health_clean <- ocs_soil_health_raw |>  
  filter(system %in% c("HF", "LF", "EWM", "RT"))

# Display cleaned dataset
kable(head(ocs_soil_health_clean))


```
#Model testing

##soil_texture_sand
```{r}

soil_texture_sand.beta <- glmmTMB(soil_texture_sand / 100 ~ system * entry + block + (1 | block:system),
                                    data = ocs_soil_health_clean,
                                    family = beta_family())

simulateResiduals(soil_texture_sand.beta,plot = TRUE) 

check_model(soil_texture_sand.beta)


```

<br>
###Anova 

```{r}
## `test_terms` is from monet and allows for a Type III anova for glmmTMB

soil_texture_sand.anova <- test_terms(formula = soil_texture_sand/100~ system * entry + block, # fixed effects go here
                                   data = ocs_soil_health_clean,
                                   extra_formula = ~ (1|block:system), # random effects go here
                                   fit_fun = glmmTMB,
                                   fit_arg = list(family = beta_family()));soil_texture_sand.anova 
                                   
soil_texture_sand.anova
                              
                                   
                               
```
<br>
### Means comparisons

```{r}
# Define model object (you can swap in different ones)
mod <- soil_texture_sand.beta

# Create a named list of comparisons and corresponding CLDs
library(emmeans)
library(multcompView)

tukey_results <- list(
  entry = emmeans(mod, pairwise ~ entry, adjust = "tukey", type = "response"),
  system = emmeans(mod, pairwise ~ system, adjust = "tukey", type = "response"),
  system_entry = emmeans(mod, list(pairwise ~ system | entry), adjust = "tukey", type = "response")
)

# Extract compact letter displays
cld_results <- list(
  entry = cld(emmeans(mod, ~entry), adjust = "tukey", type = "response", 
              Letters = letters, sort = TRUE, reversed = TRUE),
  system = cld(emmeans(mod, ~system), adjust = "tukey", type = "response", 
               Letters = letters, sort = TRUE, reversed = TRUE),
  system_entry = cld(emmeans(mod, ~system | entry), adjust = "tukey", type = "response", 
                     Letters = letters, sort = TRUE, reversed = TRUE)
)

# Access them like this:
tukey_results$entry$emmeans
tukey_results$system$emmeans
tukey_results$system_entry$emmeans
tukey_results$entry$contrasts
tukey_results$system$contrasts
tukey_results$system_entry$contrasts
cld_results$entry
cld_results$system
cld_results$system_entry
```

<br>

##soil_texture_silt
```{r}

soil_texture_silt.beta <- glmmTMB(soil_texture_silt / 100 ~ system * entry + block + (1 | block:system),
                                    data = ocs_soil_health_clean,
                                    family = beta_family())

simulateResiduals(soil_texture_silt.beta ,plot = TRUE) 

check_model(soil_texture_silt.beta )


```

###Anova 

```{r}
## `test_terms` is from monet and allows for a Type III anova for glmmTMB

soil_texture_silt.anova <- test_terms(formula = soil_texture_silt/100~ system * entry + block, # fixed effects go here
                                   data = ocs_soil_health_clean,
                                   extra_formula = ~ (1|block:system), # random effects go here
                                   fit_fun = glmmTMB,
                                   fit_arg = list(family = beta_family()));soil_texture_silt.anova 

soil_texture_silt.anova 
                                   

                               
```
<br>
### Means comparisons

```{r}
# Define model object (you can swap in different ones)
mod <- soil_texture_silt.beta


tukey_results <- list(
  entry = emmeans(mod, pairwise ~ entry, adjust = "tukey", type = "response"),
  system = emmeans(mod, pairwise ~ system, adjust = "tukey", type = "response"),
  system_entry = emmeans(mod, list(pairwise ~ system | entry), adjust = "tukey", type = "response")
)

# Extract compact letter displays
cld_results <- list(
  entry = cld(emmeans(mod, ~entry), adjust = "tukey", type = "response", 
              Letters = letters, sort = TRUE, reversed = TRUE),
  system = cld(emmeans(mod, ~system), adjust = "tukey", type = "response", 
               Letters = letters, sort = TRUE, reversed = TRUE),
  system_entry = cld(emmeans(mod, ~system | entry), adjust = "tukey", type = "response", 
                     Letters = letters, sort = TRUE, reversed = TRUE)
)

# Access them like this:
#tukey_results$entry$emmeans
#tukey_results$system$emmeans
#tukey_results$system_entry$emmeans
#tukey_results$entry$contrasts
#tukey_results$system$contrasts
#tukey_results$system_entry$contrasts
#cld_results$entry
#cld_results$system
#cld_results$system_entry
```


##soil_texture_clay
```{r}

soil_texture_clay.beta <- glmmTMB(soil_texture_clay / 100 ~ system * entry + block + (1 | block:system),
                                    data = ocs_soil_health_clean,
                                    family = beta_family())

simulateResiduals(soil_texture_clay.beta,plot = TRUE) 

check_model(soil_texture_clay.beta)


```

###Anova 

```{r}
## `test_terms` is from monet and allows for a Type III anova for glmmTMB

soil_texture_clay.anova <- test_terms(formula = soil_texture_clay/100~ system * entry + block, # fixed effects go here
                                   data = ocs_soil_health_clean,
                                   extra_formula = ~ (1|block:system), # random effects go here
                                   fit_fun = glmmTMB,
                                   fit_arg = list(family = beta_family()));soil_texture_clay.anova 

                               
```
<br>
### Means comparisons

```{r}
# Define model object (you can swap in different ones)
mod <- soil_texture_clay.beta

# Create a named list of comparisons and corresponding CLDs
library(emmeans)
library(multcompView)

tukey_results <- list(
  entry = emmeans(mod, pairwise ~ entry, adjust = "tukey", type = "response"),
  system = emmeans(mod, pairwise ~ system, adjust = "tukey", type = "response"),
  system_entry = emmeans(mod, list(pairwise ~ system | entry), adjust = "tukey", type = "response")
)

# Extract compact letter displays
cld_results <- list(
  entry = cld(emmeans(mod, ~entry), adjust = "tukey", type = "response", 
              Letters = letters, sort = TRUE, reversed = TRUE),
  system = cld(emmeans(mod, ~system), adjust = "tukey", type = "response", 
               Letters = letters, sort = TRUE, reversed = TRUE),
  system_entry = cld(emmeans(mod, ~system | entry), adjust = "tukey", type = "response", 
                     Letters = letters, sort = TRUE, reversed = TRUE)
)

# Access them like this:
tukey_results$entry$emmeans
tukey_results$system$emmeans
tukey_results$system_entry$emmeans
tukey_results$entry$contrasts
tukey_results$system$contrasts
tukey_results$system_entry$contrasts
cld_results$entry
cld_results$system
cld_results$system_entry
```




##pred_water_capacity

```{r}

pred_water_capacity.beta <- glmmTMB(pred_water_capacity ~ system * entry + block + (1 | block:system),
                                    data = ocs_soil_health_clean,
                                    family = beta_family())

simulateResiduals(pred_water_capacity.beta,plot = TRUE) 

check_model(pred_water_capacity.beta)


```

###Anova 

```{r}
## `test_terms` is from monet and allows for a Type III anova for glmmTMB

pred_water_capacity.anova <- test_terms(formula = pred_water_capacity~ system * entry + block, # fixed effects go here
                                   data = ocs_soil_health_clean,
                                   extra_formula = ~ (1|block:system), # random effects go here
                                   fit_fun = glmmTMB,
                                   fit_arg = list(family = beta_family()));pred_water_capacity.anova 


```
<br>
### Means comparisons

```{r}
# Define model object (you can swap in different ones)
mod <- pred_water_capacity.beta

# Create a named list of comparisons and corresponding CLDs
library(emmeans)
library(multcompView)

tukey_results <- list(
  entry = emmeans(mod, pairwise ~ entry, adjust = "tukey", type = "response"),
  system = emmeans(mod, pairwise ~ system, adjust = "tukey", type = "response"),
  system_entry = emmeans(mod, list(pairwise ~ system | entry), adjust = "tukey", type = "response")
)

# Extract compact letter displays
cld_results <- list(
  entry = cld(emmeans(mod, ~entry), adjust = "tukey", type = "response", 
              Letters = letters, sort = TRUE, reversed = TRUE),
  system = cld(emmeans(mod, ~system), adjust = "tukey", type = "response", 
               Letters = letters, sort = TRUE, reversed = TRUE),
  system_entry = cld(emmeans(mod, ~system | entry), adjust = "tukey", type = "response", 
                     Letters = letters, sort = TRUE, reversed = TRUE)
)

# Access them like this:
tukey_results$entry$emmeans
tukey_results$system$emmeans
tukey_results$system_entry$emmeans
tukey_results$entry$contrasts
tukey_results$system$contrasts
tukey_results$system_entry$contrasts
cld_results$entry
cld_results$system
cld_results$system_entry
```



##surface_hardness
```{r}
surface_hardness.gauss<- glmmTMB(surface_hardness~ system* entry + block + (1 | block:system),
                      data = ocs_soil_health_clean,
                      family = gaussian())


#look at the AIC
AIC(surface_hardness.gauss)

simulateResiduals(surface_hardness.gauss,plot = TRUE) 

check_model(surface_hardness.gauss)


```

### Anova 

```{r}
## `test_terms` is from monet and allows for a Type III anova for glmmTMB

surface_hardness.anova <- test_terms(formula = surface_hardness~ system * entry + block, # fixed effects go here
                                   data = ocs_soil_health_clean,
                                   extra_formula = ~ (1|block:system), # random effects go here
                                   fit_fun = glmmTMB,
                                   fit_arg = list(family = gaussian()));surface_hardness.anova 

                               
```
<br>
### Means comparisons

```{r}
# Define model object (you can swap in different ones)
mod <- surface_hardness.gauss

# Tukey HSD pairwise comparisons
tukey_results <- list(
  entry = emmeans(mod, pairwise ~ entry, adjust = "tukey", type = "response"),
  system = emmeans(mod, pairwise ~ system, adjust = "tukey", type = "response"),
  system_entry = emmeans(mod, list(pairwise ~ system | entry), adjust = "tukey", type = "response")
)

# Fisher LSD (no adjustment)
lsd_results <- list(
  entry = emmeans(mod, pairwise ~ entry, adjust = "none", type = "response"),
  system = emmeans(mod, pairwise ~ system, adjust = "none", type = "response"),
  system_entry = emmeans(mod, list(pairwise ~ system | entry), adjust = "none", type = "response")
)

# CLDs for Tukey
cld_results_tukey <- list(
  entry = cld(emmeans(mod, ~entry), adjust = "tukey", type = "response", 
              Letters = letters, sort = TRUE, reversed = TRUE),
  system = cld(emmeans(mod, ~system), adjust = "tukey", type = "response", 
               Letters = letters, sort = TRUE, reversed = TRUE),
  system_entry = cld(emmeans(mod, ~system | entry), adjust = "tukey", type = "response", 
                     Letters = letters, sort = TRUE, reversed = TRUE)
)

# CLDs for Fisher LSD
cld_results_lsd <- list(
  entry = cld(emmeans(mod, ~entry), adjust = "none", type = "response", 
              Letters = letters, sort = TRUE, reversed = TRUE),
  system = cld(emmeans(mod, ~system), adjust = "none", type = "response", 
               Letters = letters, sort = TRUE, reversed = TRUE),
  system_entry = cld(emmeans(mod, ~system | entry), adjust = "none", type = "response", 
                     Letters = letters, sort = TRUE, reversed = TRUE)
)

# Example: Accessing outputs
# Tukey
tukey_results$entry$emmeans
tukey_results$system$emmeans
tukey_results$system_entry$emmeans
tukey_results$entry$contrasts
tukey_results$system$contrasts
tukey_results$system_entry$contrasts
cld_results_tukey$entry
cld_results_tukey$system
cld_results_tukey$system_entry

# LSD
lsd_results$entry$emmeans
lsd_results$system$emmeans
lsd_results$system_entry$emmeans
lsd_results$entry$contrasts
lsd_results$system$contrasts
lsd_results$system_entry$contrasts
cld_results_lsd$entry
cld_results_lsd$system
cld_results_lsd$system_entry

```

###significant

```{r}
#`test_terms` is from monet and allows for a Type III anova for glmmTMB

surface_hardness.gamma.anova <- test_terms(formula = surface_hardness~ treatments * entry +block, #fixed effects go here
                                   data = ocs_soil_health_clean,
                                   extra_formula = ~ (1|block:treatments), # random effects go here
                                   fit_fun = glmmTMB,
                                   fit_arg = list(Gamma(link = "log"))); surface_hardness.gamma.anova  # put the family you decided on in the fit_arg
```

```{r}
# Then move on to post-hoc using emmeans if indicated by the ANOVA. The example below would be used if the System term
# alone was significant.
surface_hardness.emm <- emmeans(surface_hardness.gamma, ~treatments|entry, type="response"); pwpm(surface_hardness.emm , adjust="none")


```
```{r}
# Compute estimated marginal means for treatments within each entry
surface_hardness.emm <- emmeans(surface_hardness.gamma, ~treatments | entry, type = "response")

# Generate CLD output
cld_surface_hardness <- cld(surface_hardness.emm, Letters = letters, adjust = "none", sort = TRUE, reversed = TRUE)

# Print the results
cld_surface_hardness

```
##subsurface_hardness
```{r}
subsurface_hardness.gauss<- glmmTMB(subsurface_hardness~ treatments * entry + block + (1 | block:treatments),
                      data = ocs_soil_health_clean,
                      family = gaussian())

subsurface_hardness.gamma <- glmmTMB(subsurface_hardness~ treatments * entry + block + (1 | block:treatments),
                                     data = ocs_soil_health_clean,
                                     family = Gamma(link = "log"))

#look at the AIC
AIC(subsurface_hardness.gauss,subsurface_hardness.gamma )


ocs_soil_health_clean <- ocs_soil_health_clean |> 
  mutate(pred_water_capacity_scaled = pred_water_capacity * 100)

pred_water_capacity.gauss <- glmmTMB(pred_water_capacity_scaled ~ treatments * entry + block + (1 | block:treatments),
                                     data = ocs_soil_health_clean,
                                      family = gaussian())

AIC(pred_water_capacity.gauss) 

# The simulate residuals function comes from DHARMa and allows visual inspection of
# glmm fit. Another useful way of deciding which model you will use for this response variable.
simulateResiduals(subsurface_hardness.gamma,plot = TRUE) 

check_model(subsurface_hardness.gamma)


```
###monet annova 
###significant

```{r}
#`test_terms` is from monet and allows for a Type III anova for glmmTMB

subsurface_hardness.gamma.anova <- test_terms(formula = subsurface_hardness~ treatments * entry +block, #fixed effects go here
                                   data = ocs_soil_health_clean,
                                   extra_formula = ~ (1|block:treatments), # random effects go here
                                   fit_fun = glmmTMB,
                                   fit_arg = list(Gamma(link = "log"))); subsurface_hardness.gamma.anova  # put the family you decided on in the fit_arg
```
```{r}
# Then move on to post-hoc using emmeans if indicated by the ANOVA. The example below would be used if the System term
# alone was significant.
subsurface_hardness.emm <- emmeans(subsurface_hardness.gamma, ~treatments|entry, type="response"); pwpm(subsurface_hardness.emm , adjust="none")


```
```{r}
# Compute estimated marginal means for treatments within each entry
subsurface_hardness.emm <- emmeans(subsurface_hardness.gamma, ~treatments | entry, type = "response")

# Generate CLD output
cld_subsurface_hardness <- cld(subsurface_hardness.emm, Letters = letters, adjust = "none", sort = TRUE, reversed = TRUE)

# Print the results
cld_subsurface_hardness

```
# organic_matter(is a percentage)
```{r}



organic_matter.beta <- glmmTMB(organic_matter / 100 ~ treatments * entry + block + (1 | block:treatments),
                                    data = ocs_soil_health_clean,
                                    family = beta_family())




# The simulate residuals function comes from DHARMa and allows visual inspection of
# glmm fit. Another useful way of deciding which model you will use for this response variable.
simulateResiduals(organic_matter.beta,plot = TRUE) 

check_model(organic_matter.beta)


```
###monet annova 
###Not significant

```{r}
#`test_terms` is from monet and allows for a Type III anova for glmmTMB

# Scale organic matter percentage to (0,1)
ocs_soil_health_clean$organic_matter_scaled <- ocs_soil_health_clean$organic_matter / 100

# Fit beta regression
organic_matter.beta.anova <- test_terms(
  formula = organic_matter_scaled ~ treatments * entry + block,  # Fixed effects
  data = ocs_soil_health_clean,
  extra_formula = ~ (1|block:treatments),  # Random effects
  fit_fun = glmmTMB,
  fit_arg = list(family = beta_family())
)

organic_matter.beta.anova
```

##pred_soil_protein
```{r}
pred_soil_protein.gauss<- glmmTMB(pred_soil_protein~ treatments * entry + block + (1 | block:treatments),
                      data = ocs_soil_health_clean,
                      family = gaussian())





pred_soil_protein.gamma <- glmmTMB(pred_soil_protein~ treatments * entry + block + (1 | block:treatments),
                                     data = ocs_soil_health_clean,
                                     family = Gamma(link = "log"))


#look at the AIC
AIC(pred_soil_protein.gauss,pred_soil_protein.gamma )



# The simulate residuals function comes from DHARMa and allows visual inspection of
# glmm fit. Another useful way of deciding which model you will use for this response variable.
simulateResiduals(pred_soil_protein.gamma,plot = TRUE) 

check_model(pred_soil_protein.gamma)


```
###monet annova 
### Notsignificant

```{r}
#`test_terms` is from monet and allows for a Type III anova for glmmTMB

pred_soil_protein.gamma.anova <- test_terms(formula = pred_soil_protein~ treatments * entry +block, #fixed effects go here
                                   data = ocs_soil_health_clean,
                                   extra_formula = ~ (1|block:treatments), # random effects go here
                                   fit_fun = glmmTMB,
                                   fit_arg = list(Gamma(link = "log"))); pred_soil_protein.gamma.anova # put the family you decided on in the fit_arg
```





#Loop attempt

```{r}
## Select column names from soil_texture_sand to overall_score
soil_health_params <- names(ocs_soil_health_clean)[8:45]

# Create an empty list to store model results
soil_health_models <- list()

# Loop through each soil health parameter and fit the model
for (param in soil_health_params) {
  formula <- as.formula(paste(param, "~ treatments * entry + block + (1 | block:treatments)"))
  
  # Fit the model
  soil_health_models[[param]] <- glmmTMB(formula, 
                                         data = ocs_soil_health_clean, 
                                         family = gaussian())
}

# Print summaries for all models
walk2(soil_health_models, names(soil_health_models), ~ {
  cat("\n*** Summary for:", .y, "***\n")
  print(summary(.x))
})

```




### Joint test (anova)
```{r}
glmm_ja |> 
  joint_tests() |> 
  kable()  
```

### Fisher compact letter display
####  treatments (significant)

```{r}
cld_treatments_fisher <-cld(emmeans(glmm_ja, ~  treatments , type = "response"), Letters = letters, adjust = "none",sort = TRUE, reversed=TRUE)
cld_treatments_fisher 
```