---
title: "Ocs microarthropods"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load libraries

```{r message=FALSE, warning=FALSE}

library(tidyverse)
library(multcomp)
library(emmeans)
library(knitr)
library(patchwork) ##install.packages("patchwork")
library(skimr)     ##install.packages("skimr")
library(readxl)
library(janitor) ##install.packages("janitor")
library(kableExtra) ##install.packages("kableExtra")
library(WrensBookshelf)##install.packages("WrensBookshelf")
## For GLM modeling
library(monet)
library(DHARMa)
library(glmmTMB)
library(performance)
```

# Load and clean data

## Load data

``` {r}
ocs_invertebrates_raw <- read_excel("~/Github/OCS_microarthropods/raw-data/ocs_invertebrates_kg.xlsx")
ocs_invertebrates_raw$block <- as.factor(ocs_invertebrates_raw$block)
ocs_invertebrates_raw$entry <- as.factor(ocs_invertebrates_raw$entry)
ocs_invertebrates_raw$system <- as.factor(ocs_invertebrates_raw$system)
ocs_invertebrates_raw <- ocs_invertebrates_raw |> 
  mutate(across(where(is.numeric), round))


kable(head(ocs_invertebrates_raw))

```

##Clean data

```{r}
 #Filter relevant data (we can't use data from alley and corn)
ocs_invertebrates_clean <- ocs_invertebrates_raw |>  
  filter(system %in% c("HF", "LF", "EWM", "RT"))

# Display cleaned dataset
kable(head(ocs_invertebrates_clean))


```

##Model testing

```{r}
# Function to fit models and run diagnostics for a given response variable
test_glmm_models <- function(response_var, data) {
  
  # Define model formulas
  formula <- as.formula(paste(response_var, "~ system * entry + block + (1 | block:system)"))
  
  # Fit models with different distributions
  models <- list(
    binom1 = glmmTMB(formula, family = nbinom1(link = "log"), data = data),
    binom2 = glmmTMB(formula, family = nbinom2(link = "log"), data = data),
    poiss = glmmTMB(formula, family = poisson(link = "log"), data = data),
    tweedie = glmmTMB(formula, family = tweedie(link = "log"), data = data),
    zi = glmmTMB(formula, family = nbinom1(link = "log"), ziformula = ~ 1, data = data)
  )

  # Overdispersion check (using nbinom1)
  resid_pearson <- residuals(models$binom1, type = "pearson")
  dispersion_ratio <- sum(resid_pearson^2) / df.residual(models$binom1)
  cat("\n--- Overdispersion Check for", response_var, "---\n")
  cat("Dispersion Ratio:", round(dispersion_ratio, 2), "\n")
  
  # Zero inflation test
  sim_residuals <- simulateResiduals(models$binom1)
  zi_test <- testZeroInflation(sim_residuals)
  cat("Zero Inflation Test p-value:", zi_test$p.value, "\n")
  
  # Compare models using AIC
  aic_results <- AIC(models$binom1, models$binom2, models$poiss, models$tweedie, models$zi)
  print(aic_results)

  # Plot residual diagnostics
  plot(sim_residuals)
  
  # Check model fit visually
  check_model(models$binom1)  # Works with `performance` package
  
  return(models)  # Return models in case you want to use them later
}

```
###total_organisms

```{r}
models_total_organisms <- test_glmm_models("total_organisms", ocs_invertebrates_clean)

```

####Anova (almost significant)
```{r}
# `test_terms` is from monet and allows for a Type III anova for glmmTMB
total_organisms.binom1.anova <- test_terms(formula = total_organisms ~ system * entry + block, # fixed effects go here
                                           data = ocs_invertebrates_clean,
                                           extra_formula = ~ (1|block:system), # random effects go here
                                           fit_fun = glmmTMB,
                                           fit_arg = list(family=nbinom1(link="log"))); total_organisms.binom1.anova # put the family you decided on in the fit_arg
```
<br>

####post-hoc
```{r}
# Perform post-hoc analysis using emmeans if indicated by the ANOVA  
total_organisms.emm <- emmeans(models_total_organisms$binom1, ~system, type="response")

# Run pairwise comparisons with Tukey adjustment
tukey_results <- pairs(total_organisms.emm, adjust = "tukey")
print(tukey_results)  # Check the pairwise comparisons

# Generate CLD output with Tukey adjustment
library(multcompView)
cld_total_organisms <- cld(total_organisms.emm, Letters = letters, adjust = "tukey", sort = TRUE, reversed = TRUE)

# Print the CLD results
print(cld_total_organisms)
```

<br>

###total_collembola

```{r}
models_total_collembola <- test_glmm_models("total_collembola", ocs_invertebrates_clean)

```
####Anova (not significant)
```{r}
# `test_terms` is from monet and allows for a Type III anova for glmmTMB
total_collembola.binom1.anova <- test_terms(formula = total_collembola ~ system * entry + block, # fixed effects go here
                                           data = ocs_invertebrates_clean,
                                           extra_formula = ~ (1|block:system), # random effects go here
                                           fit_fun = glmmTMB,
                                           fit_arg = list(family=nbinom1(link="log"))); total_collembola.binom1.anova # put the family you decided on in the fit_arg
```
<br>

###entomobryidae (no models are converging)
```{r}
models_entomobryidae <- test_glmm_models("entomobryidae", ocs_invertebrates_clean)

sum(ocs_invertebrates_clean$entomobryidae == 0)  # Observed zeros
sum(sim_zeros$simulatedResponse == 0)  # Simulated zeros under NB model
```

<br>

###isotomidae 
```{r}
models_isotomidae <- test_glmm_models("isotomidae", ocs_invertebrates_clean)

```

<br>

####anova (not significant)
```{r}
# `test_terms` is from monet and allows for a Type III anova for glmmTMB
isotomidae.binom1.anova <- test_terms(formula = isotomidae ~ treatments * entry + block, # fixed effects go here
                                           data = ocs_invertebrates_clean,
                                           extra_formula = ~ (1|block:treatments), # random effects go here
                                           fit_fun = glmmTMB,
                                           fit_arg = list(family=nbinom1(link="log"))); isotomidae.binom1.anova # put the family you decided on in the fit_arg
```

<br>

###onychiuridae (treatment is significant)
```{r}
models_onychiuridae  <- test_glmm_models("onychiuridae ", ocs_invertebrates_clean)

onychiuridae.tweedie <- glmmTMB(
 onychiuridae ~ treatments * entry + block + (1 | block:treatments),
  family = tweedie(link = "log"),
  data = ocs_invertebrates_clean
)

onychiuridae_zi <- glmmTMB(
  onychiuridae ~ treatments * entry + block + (1 | block:treatments),
  family = nbinom1(link = "log"),
  ziformula = ~ 1,  # Tests if zero inflation is needed
  data = ocs_invertebrates_clean
)

# Diagnostic residual plots (for best model selection)
res.onychiuridae <- simulateResiduals(onychiuridae.tweedie, n = 1000, integerResponse = FALSE)
plot(res.onychiuridae)

# Check overall model fit visually
check_model(onychiuridae.tweedie)  # Works with `performance` package

```


######anova (significant)
```{r}
# `test_terms` is from monet and allows for a Type III anova for glmmTMB
onychiuridae.tweedie.anova <- test_terms(formula = onychiuridae ~ treatments * entry + block, # fixed effects go here
                                           data = ocs_invertebrates_clean,
                                           extra_formula = ~ (1|block:treatments), # random effects go here
                                           fit_fun = glmmTMB,
                                           fit_arg = list(family=tweedie(link="log"))); onychiuridae.tweedie.anova # put the family you decided on in the fit_arg
```

######post-hoc
```{r}
# Then move on to post-hoc using emmeans if indicated by the ANOVA. 
onychiuridae.emm <- emmeans(onychiuridae.tweedie, ~treatments, type="response"); pwpm(onychiuridae.emm , adjust="none")

# Generate CLD output
cld_onychiuridae <- cld(onychiuridae.emm, Letters = letters, adjust = "none", sort = TRUE, reversed = TRUE)

# Print the results
cld_onychiuridae



```

```{r message=FALSE}
ocs_invertebrates_clean |> 
  left_join(cld_onychiuridae) |> 
  ggplot(aes(x = factor(treatments, levels = c("HF", "LF", "EWM", "RT")), 
             y = response, fill = treatments)) +
  geom_bar(stat = "identity", position = position_dodge()) + 
  geom_errorbar(aes(ymin = response - SE, ymax = response + SE), 
                width = 0.2, position = position_dodge(0.9)) +
  geom_text(aes(label = trimws(.group), y = response + SE + 0.75), 
            size = 7) +
  labs(
    x = "",
    y = expression("Density" ~ (individuals ~ kg^{-1} ~ "dry soil")),
    subtitle = expression(italic("P < 0.05"))
  ) +
  scale_x_discrete(labels = c("High\nfertility", "Low\nfertility", 
                              "Enhanced\nweed\nmanagement", "Reduced\ntillage")) +
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.3))) +
  scale_fill_WB_d(name = "BlueberriesForSal", direction = 1) +
  theme_bw() +
  theme(
    legend.position = "none",
    strip.background = element_blank(),
    strip.text = element_text(face = "bold", size = 12),
    axis.title = element_text(size = 24),
    axis.text = element_text(size = 16),
    plot.subtitle = element_text(size = 24, face = "italic")
  )
ggsave("onychiuridae_kg.png", width = 10, height = 6, dpi = 300)
```
#####sminthuridae (not enough data)
```{r}
models_sminthuridae <- test_glmm_models("sminthuridae", ocs_invertebrates_clean)

# Diagnostic residual plots (for best model selection)
res.onychiuridae <- simulateResiduals(onychiuridae.tweedie, n = 1000, integerResponse = FALSE)
plot(res.onychiuridae)

# Check overall model fit visually
check_model(onychiuridae.tweedie)  # Works with `performance` package

```





###total_mites, low zero inflation, treatment by entry is significant!
```{r}
models_total_mites <- test_glmm_models("total_mites", ocs_invertebrates_clean)


```

####anova (significant)
```{r}
# `test_terms` is from monet and allows for a Type III anova for glmmTMB
total_mites.binom1.anova <- test_terms(formula = total_mites ~ treatments * entry + block, # fixed effects go here
                                           data = ocs_invertebrates_clean,
                                   extra_formula = ~ (1|block:treatments), # random effects go here
                                    fit_fun = glmmTMB,
                                   fit_arg = list(family=nbinom1(link="log"))); total_mites.binom1.anova # put the family you decided on in the fit_arg
```

```{r}
# Then move on to post-hoc using emmeans if indicated by the ANOVA. 
total_mites.emm <- emmeans(models_total_mites$binom1, ~treatments|entry, type="response"); pwpm(total_mites.emm , adjust="none")

# Generate CLD output
cld_total_mites <- cld(total_mites.emm, Letters = letters, adjust = "none", sort = TRUE, reversed = TRUE)

# Print the results
cld_total_mites


```


```{r message=FALSE}
ocs_invertebrates_clean |> 
  left_join(cld_total_mites) |> 
  ggplot(aes(x = factor(treatments, levels = c("HF", "LF", "EWM", "RT")), 
             y = response, fill = treatments)) +
  facet_wrap(~entry, labeller = labeller(
    entry = c("A" = "Entry Point A", "B" = "Entry Point B")
  )) +
  geom_bar(stat = "identity", position = position_dodge()) + 
  geom_errorbar(aes(ymin = response - SE, ymax = response + SE), 
                width = 0.2, position = position_dodge(0.9)) +
  geom_text(aes(label = trimws(.group), y = response + SE + 3), 
            size = 7) +
  labs(
    x = "",
    y = expression("Density" ~ (individuals ~ kg^{-1} ~ "dry soil")),
    subtitle = expression(italic("P < 0.005"))
  ) +
  scale_x_discrete(labels = c("High\nfertility", "Low\nfertility", 
                              "Enhanced\nweed\nmanagement", "Reduced\ntillage")) +
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.3))) +
  scale_fill_WB_d(name = "BlueberriesForSal", direction = 1) +
  theme_bw() +
  theme(
    legend.position = "none",
    strip.background = element_blank(),
    strip.text = element_text(face = "bold", size = 12),
    axis.title = element_text(size = 24),
    axis.text = element_text(size = 16),
    plot.subtitle = element_text(size = 24, face = "italic")
  )
ggsave("total_mites_kg.png", width = 10, height = 6, dpi = 300)
```


#######total_astigmata, 
```{r}

models_total_astigmata <- test_glmm_models("total_astigmata", ocs_invertebrates_clean)

# Diagnostic residual plots (for best model selection)
res.total_astigmata <- simulateResiduals(models_total_astigmata$poiss, n = 1000, integerResponse = FALSE)
plot(res.total_astigmata)

# Check overall model fit visually
check_model(models_total_astigmata$poiss)  # Works with `performance` package

```
#######anova (significant)
```{r}
# `test_terms` is from monet and allows for a Type III anova for glmmTMB
total_astigmata.poiss.anova <- test_terms(formula = total_astigmata ~ treatments * entry + block, # fixed effects go here
                                           data = ocs_invertebrates_clean,
                                   extra_formula = ~ (1|block:treatments), # random effects go here
                                    fit_fun = glmmTMB,
                                   fit_arg = list(family=poisson(link="log"))); total_astigmata.poiss.anova # put the family you decided on in the fit_arg
```

```{r}
# Then move on to post-hoc using emmeans if indicated by the ANOVA. 
total_astigmata.emm <- emmeans(models_total_astigmata$poiss, ~treatments|entry, type="response"); pwpm(total_astigmata.emm , adjust="none")

# Generate CLD output
cld_total_astigmata <- cld(total_astigmata.emm, Letters = letters, adjust = "none", sort = TRUE, reversed = TRUE)

# Print the results
cld_total_astigmata


```

```{r message=FALSE}
ocs_invertebrates_clean |> 
  left_join(cld_total_astigmata) |> 
  ggplot(aes(x = factor(treatments, levels = c("HF", "LF", "EWM", "RT")), 
             y = rate, fill = treatments)) +
  facet_wrap(~entry, labeller = labeller(
    entry = c("A" = "Entry Point A", "B" = "Entry Point B")
  )) +
  geom_bar(stat = "identity", position = position_dodge()) + 
  geom_errorbar(aes(ymin = rate - SE, ymax = rate + SE), 
                width = 0.2, position = position_dodge(0.9)) +
  geom_text(aes(label = trimws(.group), y = rate + SE + 1), 
            size = 7) +
  labs(
    x = "",
    y = expression("Density" ~ (individuals ~ kg^{-1} ~ "dry soil")),
    subtitle = expression(italic("P < 0.005"))
  ) +
  scale_x_discrete(labels = c("High\nfertility", "Low\nfertility", 
                              "Enhanced\nweed\nmanagement", "Reduced\ntillage")) +
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.3))) +
  scale_fill_WB_d(name = "BlueberriesForSal", direction = 1) +
  theme_bw() +
  theme(
    legend.position = "none",
    strip.background = element_blank(),
    strip.text = element_text(face = "bold", size = 12),
    axis.title = element_text(size = 24),
    axis.text = element_text(size = 16),
    plot.subtitle = element_text(size = 24, face = "italic")
  )
ggsave("total_astigmata_kg.png", width = 10, height = 6, dpi = 300)
```




#######total_mesostigmata, Treatment by Entry is significant
```{r}

models_total_mesostigmata <- test_glmm_models("total_mesostigmata", ocs_invertebrates_clean)

# Diagnostic residual plots (for best model selection)
res.total_mesostigmata <- simulateResiduals(models_total_mesostigmata$tweedie, n = 1000, integerResponse = FALSE)
plot(res.total_mesostigmata)

# Check overall model fit visually
check_model(models_total_mesostigmata$tweedie)  # Works with `performance` package


```
```{r}
# `test_terms` is from monet and allows for a Type III anova for glmmTMB
total_mesostigmata.tweedie.anova <- test_terms(formula = total_mesostigmata ~ treatments * entry + block, # fixed effects go here
                                           data = ocs_invertebrates_clean,
                                   extra_formula = ~ (1|block:treatments), # random effects go here
                                    fit_fun = glmmTMB,
                                   fit_arg = list(family=tweedie(link="log"))); total_mesostigmata.tweedie.anova# put the family you decided on in the fit_arg
```

```{r}
# Then move on to post-hoc using emmeans if indicated by the ANOVA. 
total_mesostigmata.emm <- emmeans(models_total_mesostigmata$tweedie, ~treatments|entry, type="response"); pwpm(total_mesostigmata.emm , adjust="none")

# Generate CLD output
cld_total_mesostigmata <- cld(total_mesostigmata.emm, Letters = letters, adjust = "none", sort = TRUE, reversed = TRUE)

# Print the results
cld_total_mesostigmata


```

```{r message=FALSE}
ocs_invertebrates_clean |> 
  left_join(cld_total_mesostigmata) |> 
  ggplot(aes(x = factor(treatments, levels = c("HF", "LF", "EWM", "RT")), 
             y = response, fill = treatments)) +
  facet_wrap(~entry, labeller = labeller(
    entry = c("A" = "Entry Point A", "B" = "Entry Point B")
  )) +
  geom_bar(stat = "identity", position = position_dodge()) + 
  geom_errorbar(aes(ymin = response - SE, ymax = response + SE), 
                width = 0.2, position = position_dodge(0.9)) +
  geom_text(aes(label = trimws(.group), y = response + SE + 0.75), 
            size = 7) +
  labs(
    x = "",
     y = expression("Density" ~ (individuals ~ kg^{-1} ~ "dry soil")),
    subtitle = expression(italic("P < 0.05"))
  ) +
  scale_x_discrete(labels = c("High\nfertility", "Low\nfertility", 
                              "Enhanced\nweed\nmanagement", "Reduced\ntillage")) +
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.3))) +
  scale_fill_WB_d(name = "BlueberriesForSal", direction = 1) +
  theme_bw() +
  theme(
    legend.position = "none",
    strip.background = element_blank(),
    strip.text = element_text(face = "bold", size = 12),
    axis.title = element_text(size = 24),
    axis.text = element_text(size = 16),
    plot.subtitle = element_text(size = 24, face = "italic")
  )
ggsave("total_mesostigmata_kg.png", width = 10, height = 6, dpi = 300)
```
#######total_oribatida, Not significant

```{r}
models_total_oribatida <- test_glmm_models("total_oribatida", ocs_invertebrates_clean)

# Diagnostic residual plots (for best model selection)
res.total_oribatida <- simulateResiduals(models_total_oribatida$tweedie, n = 1000, integerResponse = FALSE)
plot(res.total_oribatida)

# Check overall model fit visually
check_model(models_total_oribatida$tweedie)  # Works with `performance` package


```
######anova (not significant)
```{r}
# `test_terms` is from monet and allows for a Type III anova for glmmTMB
total_oribatida.binom1.anova <- test_terms(formula = total_oribatida ~ treatments * entry + block, # fixed effects go here
                                           data = ocs_invertebrates_clean,
                                   extra_formula = ~ (1|block:treatments), # random effects go here
                                    fit_fun = glmmTMB,
                                   fit_arg = list(family=nbinom1(link="log"))); total_oribatida.binom1.anova# put the family you decided on in the fit_arg
```

#######phoretic_hypopi, 

```{r}
models_phoretic_hypopi <- test_glmm_models("phoretic_hypopi", ocs_invertebrates_clean)

```

####Anova (almost significant)
```{r}
# `test_terms` is from monet and allows for a Type III anova for glmmTMB
phoretic_hypopi.binom1.anova <- test_terms(formula = phoretic_hypopi ~ treatments * entry + block, # fixed effects go here
                                           data = ocs_invertebrates_clean,
                                           extra_formula = ~ (1|block:treatments), # random effects go here
                                           fit_fun = glmmTMB,
                                           fit_arg = list(family=nbinom1(link="log"))); phoretic_hypopi.binom1.anova # put the family you decided on in the fit_arg
```
```{r}
# Then move on to post-hoc using emmeans if indicated by the ANOVA. 
phoretic_hypopi.emm <- emmeans(models_phoretic_hypopi$binom1, ~treatments|entry, type="response"); pwpm(phoretic_hypopi.emm , adjust="none")

# Generate CLD output
cld_phoretic_hypopi <- cld(phoretic_hypopi.emm, Letters = letters, adjust = "none", sort = TRUE, reversed = TRUE)

# Print the results
cld_phoretic_hypopi


```

```{r message=FALSE}
ocs_invertebrates_clean |> 
  left_join(cld_phoretic_hypopi) |> 
  ggplot(aes(x = factor(treatments, levels = c("HF", "LF", "EWM", "RT")), 
             y = response, fill = treatments)) +
  facet_wrap(~entry, labeller = labeller(
    entry = c("A" = "Entry Point A", "B" = "Entry Point B")
  )) +
  geom_bar(stat = "identity", position = position_dodge()) + 
  geom_errorbar(aes(ymin = response - SE, ymax = response + SE), 
                width = 0.2, position = position_dodge(0.9)) +
  geom_text(aes(label = trimws(.group), y = response + SE + 1.5), 
            size = 7) +
  labs(
    x = "",
     y = expression("Density" ~ (individuals ~ kg^{-1} ~ "dry soil")),
    subtitle = expression(italic("P < 0.05"))
  ) +
  scale_x_discrete(labels = c("High\nfertility", "Low\nfertility", 
                              "Enhanced\nweed\nmanagement", "Reduced\ntillage")) +
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.3))) +
  scale_fill_WB_d(name = "BlueberriesForSal", direction = 1) +
  theme_bw() +
  theme(
    legend.position = "none",
    strip.background = element_blank(),
    strip.text = element_text(face = "bold", size = 12),
    axis.title = element_text(size = 24),
    axis.text = element_text(size = 16),
    plot.subtitle = element_text(size = 24, face = "italic")
  )
ggsave("phoretic_hypopi_kg.png", width = 10, height = 6, dpi = 300)
```





```{r}
# Function to fit models and run diagnostics for a given response variable
test_glmm_models <- function(response_var, data) {
  
  # Define model formulas
  formula <- as.formula(paste(response_var, "~ treatments * entry + block + (1 | block:treatments)"))
  
  # Fit models with different distributions
  models <- list(
    binom1 = glmmTMB(formula, family = nbinom1(link = "log"), data = data),
    binom2 = glmmTMB(formula, family = nbinom2(link = "log"), data = data),
    poiss = glmmTMB(formula, family = poisson(link = "log"), data = data),
    tweedie = glmmTMB(formula, family = tweedie(link = "log"), data = data),
    zi = glmmTMB(formula, family = nbinom1(link = "log"), ziformula = ~ 1, data = data)
  )

  # Overdispersion check (using nbinom1)
  resid_pearson <- residuals(models$binom1, type = "pearson")
  dispersion_ratio <- sum(resid_pearson^2) / df.residual(models$binom1)
  cat("\n--- Overdispersion Check for", response_var, "---\n")
  cat("Dispersion Ratio:", round(dispersion_ratio, 2), "\n")
  
  # Zero inflation test
  sim_residuals <- simulateResiduals(models$binom1)
  zi_test <- testZeroInflation(sim_residuals)
  cat("Zero Inflation Test p-value:", zi_test$p.value, "\n")
  
  # Compare models using AIC
  aic_results <- AIC(models$binom1, models$binom2, models$poiss, models$tweedie, models$zi)
  print(aic_results)

  # Plot residual diagnostics
  plot(sim_residuals)
  
  # Check model fit visually
  check_model(models$binom1)  # Works with `performance` package
  
  return(models)  # Return models in case you want to use them later
}

# Run the function for total_oribatida
models_total_oribatida <- test_glmm_models("total_oribatida", ocs_invertebrates_clean)


```

